Blocking-resistant communication\\through domain fronting

### 2014-07-30 docs/meek.tex
Typo.
Escape spaces after "\meek".
You need this, otherwise the escape sequence eats the space. I.e.,
	\meek combines fronting with a proxy server
renders as
	meekcombines fronting with a proxy server

We have implemented domain fronting in a system called \meek,
a pluggable transport for Tor.
\meek combines fronting with a proxy server that encodes a TCP stream
as a sequence of HTTP requests and responses.
The \meek server's external interface is that of an ordinary web server.
Communication with it is enabled through domain fronting.
The server receives requests, decodes them, and feeds their payloads into a Tor relay,
and returns downstream data in the HTTP response.
A censor watching the communication sees only a sequence of HTTPS requests to an allowed domain.
but which actually arrive at a special web server on a Tor relay.
\meek, or something based on it,
has been adopted by other circumvention systems including Lantern and Psiphon.

@@

We have developed domain fronting into a full-fledged circumvention system called \meek,
implemented as a Tor pluggable transport~\cite{pt}.
\meek combines fronting with an HTTP-based tunneling proxy:
upstream data are transformed into a sequence of HTTP requests,
which are fronted in order to reach a proxy server.
The server decodes the requests and feeds their payloads
into a local Tor relay.
Downstream data received from the Tor relay
are returned to the client as HTTP responses
through the same fronted channel.
\meek's architecture appears in Figure~\ref{fig:architecture}.
Section~\ref{sec:architecture} describes its workings in detail.

@@

\meek has been built into an alpha version of Tor Browser,
and has seen use by a small number of users.
Our deployment uses Google App Engine,
with the hidden actual domain \urll{meek-reflect.appspot.com}
hidden by the front \urll{www.google.com}.
Section~\ref{sec:deployment} discusses other systems \meek can work with
and other deployment scenarios.
In addition to the Tor pluggable transport,
systems based on \meek are now in use by other circumvention systems
including Psiphon~\cite{psiphon} and Lantern~\cite{lantern}.

% \meek is designed to have features attractive in a circumvention transport.
% It is easy to use, not requiring the configuration of any bridge addresses.
% In Tor Browser, users need only select ``meek''
% from a pulldown menu in order to use it.
% It resists blocking by address and by content,
% Section~\ref{sec:discussion}

Domain fronting and HTTPS take care of two big circumvention challenges,
namely hiding the destination and obscuring the contents of the message.
There remain other, more subtle, meta-attributes of communication
that could serve as a basis for blocking.
For example, the handshake is a fingerprintable part of TLS.
Section~\ref{sec:browserextension} describes how we use a web browser extension as an instrument for making HTTPS requests,
in order that \meek's TLS and HTTPS characteristics
match those of a browser as closely as possible.
One of our goals for \meek is to force the censor
to employ more sophisticated, expensive, and error-prone statistical tests
to classify traffic as allowed or prohibited,
rather than simple domain blacklists or deep packet inspection;
to force the frontier of censorship
to be a frontier not of simple in-line packet filters,
but of probabilities and false positives.
A preliminary analysis of \meek's resistance to detection
based on traffic characteristics like packet size and timing
appears in Section~\ref{sec:trafficanalysis}.
The analysis is based on comparing traffic traces of \meek
with samples of HTTPS traffic at an Internet router.

@@

Flash proxy~\cite{flashproxy} resists address blocking by
conscripting web users as temporary proxies. Proxies last only as long as a web
user stays on a page, so the pool of proxies is constantly changing.
If one of them is blocked, there is soon another to replace it.
Flash proxy's approach to address blocking is in a sense
the opposite of \meek's:
where flash proxy uses many cheap, disposable, individually blockable proxies,
\meek uses just a few high-value front domains on hard-to-block network infrastructure.
A quirk of the browser proxy model is that
the client must be able to receive a TCP connection; in particular it
must not be behind network address translation~(NAT), which limits flash proxy's usefulness.
Part of the flash proxy protocol requires the client to send
a small amount of unblockable data in a process called rendezvous.
The default rendezvous mechanism has used domain fronting through App Engine since 2013~\cite{flashproxy-reg-appspot}.
Flash proxy itself does nothing to defend against DPI.
Connections between censored clients and browser-based proxies use
WebSocket, a meta-protocol running on HTTP,
but inside the WebSocket framing is the ordinary Tor protocol.
% There exists a prototype transport that attempts to get both
% content-based and address-based blocking resistance by obfuscating traffic
% with obfsproxy before sending it through flash proxy~\cite{obfs-flash}.
% However it is limited because it is not
% possible to obfuscate the outermost WebSocket layer;
% the censor could decide simply to block all WebSocket.

@@

GoAgent~\cite{goagent} is a direct inspiration for \meek in its use of App
Engine and Host header--based domain fronting.
Traffic is fronted by the Google frontend server
and delivered to its destination by a specialized app running on App Engine.
GoAgent uses the ``domainless'' fronting model without SNI for most target domains.
GoAgent doesn't use an additional general-purpose proxy after fronting;
rather, HTTP and HTTPS URLs are fetched directly from the App Engine servers,
meaning that GoAgent is limited to carrying HTTP and HTTPS traffic,
and the contents of all communications are revealed to App Engine.
Users of GoAgent upload their own personal copy of the proxy code to App Engine,
which is free of charge as long as they do not exceed a bandwidth quota.
According to a May 2013 survey~\cite{collateral-freedom},
GoAgent was the circumvention tool most used in
China, with 35\% of survey respondents having used it in the previous month.
This figure is higher than that of paid~(29\%) and free VPNs~(18\%), and far
above that of other special-purpose tools like Tor~(2.9\%) and Psiphon~(2.5\%).
Use of GoAgent in China was disrupted starting in the beginning of June~2014
when all Google services (including GoAgent's front domains) were blocked~\cite{cn-google-block}.
\meek over App Engine was similarly affected.
% Users identified reliability, speed, and ease of installation as the most important features of a circumvention tool.

@@

Psiphon~\cite{psiphon} is a network of many one-hop proxies,
with encryption and traffic obfuscation between client and server.
Psiphon uses domain fronting based on \meek as one of its blocking defenses since June~2014~\cite{psiphon-meek-merge}.
Lantern~\cite{lantern} uses a network of proxies running on volunteer computers;
proxy addresses are shared only with trusted friends in order to make them difficult to enumerate.
Lantern~1.4 is planned to use domain fronting inspired by \meek~\cite{lantern-1.3.1}.

@@

% CORDON? Say how \meek would be classified in it?

@@

Section~\ref{sec:discussion} shows what happens when some
of these assumptions are violated;
specifically what happens
when the intermediate web service's frontend server is inside the censor's network
and when the censor controls a certificate authority.
That section also describes the use of \meek apart from Tor.

@@

The components of the system are shown in Figure~\ref{fig:architecture}.
The parts that are new in \meek
are the programs \meekclient\ and \meekserver,
which are the pluggable-transports~\cite{pt} interface between Tor and \meek.
% All the programs are free software, naturally,
% and may be downloaded from the \meek home page at
% \url{https://trac.torproject.org/projects/tor/wiki/doc/meek}.

@@

When \meek is used with Google App Engine, one other component is needed.
It is a small ``reflector'' web app that simply copies any request
it receives and forwards it to an instance of \meekserver\ running on a bridge.
App Engine cannot directly run a Tor bridge,
so we bounce the requests to somewhere that can.
The reflector app emulates the behavior of an origin-pull CDN,
which also simply copies and forwards a request to the origin server
when the response is not already cached.

The main technical challenge is handling a TCP stream
that has been split up into a sequence of HTTP requests and responses.
The body of each HTTP request and HTTP response carries
a small chunk of upstream or downstream communication.
\meekserver\ must handle many clients at once,
and therefore maintains many open connections to the local Tor process,
one for each active client.
When a new request arrives, the server must determine which
open session it belongs to
(or whether it is a brand-new client needing a new session).
In TCP, different streams are distinguished by their
(source~IP, source port, dest~IP, dest~port) tuple,
but that doesn't work for \meek for two reasons:
the source IP of the requests is that of the intermediate web service,
not that of the client;
and a logical stream is chopped into multiple independent HTTP requests,
so the source port is always changing.
Rather, each client generates a random 256-bit session ID,
which it sends with each of its requests in a special
X-Session-Id header.
\meekserver, when it sees a session ID for the first time,
opens up a new connection to the local Tor process
and associates the connection and ID in a cache.
Subsequent requests with the
same session ID will reuse the same Tor connection.
Sessions are closed after a period of inactivity.
Figure~\ref{fig:protocol} shows a sample of the protocol.

@@

\x14\x03\x03\x00\x01\x01\x16\x03\x03\x00\x40\x06\x84\x25...
\end{verbatim}
\end{quote}
\caption{
Requests and responses in the \meek HTTP protocol.
The session ID is randomly generated by the client.
Request/response bodies contain successive chunks of a Tor TLS stream
(\texttt{\textbackslash{}x16\textbackslash{}x03\textbackslash{}x01\textbackslash{}x02}
is the beginning of a TLS ClientHello message).
The second POST request is an empty polling request.
The messages shown here is encrypted inside HTTPS until after
it has been fronted,
so the censor cannot use the
Host and X-Session-Id headers for classification.
}
\label{fig:protocol}
\end{figure}

The underlying TCP stream is broken into chunks so that
There must therefore be some way of making sure that chunks
are correctly reassembled at the other end,
in order and without gaps and duplicates.
\meek takes a naive approach: requests and responses are strictly serialized.
The client doesn't send a second chunk of data
(i.e, make another HTTPS request) until it has
receive the response to the first request.
The underlying stream is simply the concatenation
of chunks in the order they arrive.
Doing it this way is simple and guarantees correctness,
but has performance drawbacks because there is a full round-trip
between every send.
The performance drawbacks are not inherent to the design:
it is domain fronting, not HTTP encoding, that is the fundamental strength of the system.
Section~\ref{sec:futurework} describes more efficient encodings
that enable multiple requests in parallel.

HTTP is fundamentally a request-based protocol.
There is no way for the server to ``push'' data to the client without
having first received a request.
In order to enable the server to send back data,
\meek uses one of two techniques.
The first is polling:
every so often the client sends a request with an empty payload
if it has nothing else to send.
The polling interval starts short (100~ms) and grows exponentially
up to a maximum of 5~s.
% Implemented in Psiphon's version.
The other technique,
implemented in Psiphon's version of \meek,
uses long-lived persistent HTTP connections.
When the server sends a response, it keeps the connection open,
continually appending data to the response body while it has anything to send.
When the server receives a new request from the same client,
it closes any response it has open to the client and starts a new response.
This second technique doesn't work on all services:
notably Google App Engine doesn't support streaming downloads of this kind.

@@

Figure~\ref{fig:ciphersuites} shows examples of how TLS client
implementations may differ.
\meekclient\ is written in the Go programming language,
which has a custom TLS library~\cite{golang-crypto/tls};
Figure~\ref{fig:ciphersuites:golang}
shows how it would appear with no TLS camouflage.
Figures~\ref{fig:ciphersuites:firefox} and~\ref{fig:ciphersuites:chrome},
which are browsers, are different; the browsers are also unlike each other.
A censor could block an uncamouflaged \meek using Go's fingerprint,
if it considered the collateral damage resulting from blocking other Go programs to be slight enough.

@@

The use of a browser extension brings benefits beyond TLS camouflage.
It means \meek inherits other traffic characteristics of the browser:
for instance
how often it resolves DNS names,
its connection reuse,
and its HTTP keepalive behavior.
The Firefox extension has special advantages
when \meek is used with Tor Browser
because Tor Browser
is a modified version of Firefox.
We can use the same browser executable for both the browser the user interacts with (Tor Browser)
and the one providing TLS camouflage (a headless Firefox),
saving space in distribution packages
and sparing the user from having to separately configure a browser to run the extension.
In Tor Browser,
the headless Firefox is started and stopped transparently
when \meek is activated and deactivated.

@@

CloudFlare (\url{https://www.cloudflare.com/}),
not to be confused with CloudFront,
is a CDN also marketed as protection against
denial-of-service attacks.
It appears that any domain name on CloudFlare
can front for any other, even custom domains;
however it is not obvious which one is best to use as a front.
The front domain needs to be popular
(causing high collateral damage if blocked),
or else the censor may call our bluff and simply block the domain entirely.
It is doubly bad if that happens because not only is circumvention foiled,
some unsuspecting third part has just had their web site blocked.
A solution may be to round-robin through
a pool of domain names;
or to use ``domainless'' fronting that doesn't send SNI.
Though CloudFlare supports domain fronting,
its terms of service~\cite{cloudflare-terms}
seem to prohibit the kind of tunneled proxying that \meek does:
\begin{quote}
\textsc{Section 10: Limitation on non-HTML caching}\\
You acknowledge that CloudFlare's Service is offered as a platform to cache and
serve web pages and websites and is not offered for other purposes
\ldots\ you understand and agree to use the Service solely
for the purpose of hosting and serving web pages\ldots
\end{quote}

@@

One of our goals in developing \meek is to force
the censor to use relatively expensive statistical classifiers
to effect blocking---generally, to increase the cost of censorship.
We believe \meek as described is resistant to the ``easy''
forms of blocking, namely IP address and DNS blocking,
simple pattern-based DPI,
and active probing.
We hope that the censor will have to resort to measuring
more subtle features of the communication like
the packet length distribution and interpacket timing,
or injecting traffic at the risk of causing collateral damage.
In this section we provide a preliminary analysis
of \meek's resistance to such attacks.
Specifically, we consider three traffic features:
packet length distribution,
number of simultaneous connections,
and connection lifetime.

The issue of statistical traffic anaysis is a general one~\cite{trafficmorphing},
and mostly orthogonal to \meek's main idea, domain fronting.
It may be that the problem is
best solved by a modular component not
necessarily specifically designed for \meek.

% Advantage is that we are probably proxying web traffic.
As \meek is based on HTTPS,
we compare traffic traces of \meek against
traces of ``ordinary'' HTTPS traffic.
We did a packet capture
automatically browsing the home pages
of the top 500 Alexa web sites using \meek,
with a firewall in place so that no extraneous traffic was included.
The used \meek in Tor Browser,
with the browser camouflage described in Section~\ref{sec:browserextension},
and Google App Engine as the intermediate web service.
The \meek trace is 687~megabytes in all
and covers about 4.5 hours of network activity.
Our representative of ordinary HTTPS traffic
is a sanitized trace of 10 minutes of HTTPS traffic
% anon
from Lawrence Berkeley National Laboratory (LBL),
comprising data to and from TCP port 443 on any Google server.
% Mention the non-google if it appears in a figure.
The trace contains packet headers only, not payloads
were replaced by an incrementing counter.
The LBL trace consists 313~megabytes of packet headers,
not payloads, destined for TCP port 443 on any Google server.
The original IP addresses were masked by being
replaced by a counter before we received the trace.

\begin{figure}
\centering
\includegraphics[width=\linewidth]{datalen.pdf}
\caption{
Comparison of TCP payload length distributions
between ordinary HTTPS connections to Google services
from the LBL traffic trace,
and \meek running on App Engine, fronted through www.google.com.
% The histogram's bin width is 5~bytes.
}
\label{fig:datalen}
\end{figure}

\subsection{Packet length}
Figure~\ref{fig:datalen}
compares the packet length distribution of both traces in both directions.
Table~\ref{tab:datalen} summarizes the most common values.
In both traces, about 38\% of packets have an empty payload, mostly ACKs.
There is a small peak at the usual TCP Maximum Segment Size
of 1460 bytes.
The concentration of values near 1418 bytes
may be caused by Google servers' sizing of TLS records so they fit within TCP segments.
% https://github.com/joyent/node/issues/6889
% http://mailman.nginx.org/pipermail/nginx-devel/2013-December/004703.html
Conspicuous in the \meek trace are a small number of
likely packet sizes,
and the lack of a cluster of small payload lengths of around 50 bytes.
Both of these characteristics are probably artifacts
of Tor's fixed cell size and the nearly fixed-size HTTP headers
added by \meekclient\ and \meekserver.

% Output of datalen.R.
%
% LBL
%          0       1430       1418         41       1416       1460       1260
% 0.37665361 0.09120402 0.08493944 0.06090732 0.03101247 0.02941974 0.02021770
%       1400       1359         33
% 0.01673740 0.01126137 0.01100281
%
% meek
%        1418           0        1460         396         196        1024
% 0.405280243 0.376703906 0.071561089 0.019905460 0.018484996 0.014868083
%         811         783         151        1263
% 0.012312668 0.007811963 0.007031241 0.006569205
\begin{table}[ht]
\normalsize
\centering
\begin{tabular}{r r >{\qquad} r r}
\multicolumn{2}{c}{LBL Google HTTPS} & \multicolumn{2}{>{\qquad}c}{\meek on App Engine} \\
0 bytes & 37.6\% & 1418 bytes & 40.5\% \\
1430 bytes & 9.1\% & 0 bytes & 37.7\% \\
1418 bytes & 8.5\% & 1460 bytes & 7.2\% \\
41 bytes & 6.1\% & 396 bytes & 2.0\% \\
1416 bytes & 3.1\% & 196 bytes & 1.8\% \\
1460 bytes & 2.9\% & 1024 bytes & 1.5\%
\end{tabular}
\caption{The most common TCP payload lengths.}
\label{tab:datalen}
\end{table}

% David: I don't think the following paragraph is true.
% Almost all the length>1400 packets are Google→client, not client→Google,
% as you can see if you split the histogram up by direction.
%
% To explain the phenomenon, recall that we use browsers to handle HTTPS connections for \meek in order
% to hide TLS handshake characteristics.
% Browsers also apply techniques like HTTP pipelining to improve performance. Since \meek is always communicating with
% the same Google frontend server, the browser will keep the persistent TLS connection. In addition, small requests 
% can be batched into a large chunk before being sent. This explains why large packets are mostly seen from the trace that
% records \meek's traffic.
% In contrast, normal users may not have persistent connections to Google. For example, a user may search a keyword on
% Google, click a result, and then close the tab that displays search results. The browser may close the 
% connection immediately after the user leaves the Google web page. Next time the user browses Google search, the browser 
% opens a new connection. In this case, small requests do not have such opportunity for batching.

% These browser techniques improve performance, but also pose unexpected consequences. 
% Although \meek alters the packet size distribution of underlying Tor traffic, 
% the censor may be aware of the distribution of \meek itself. 
% Additionally, the persistent connection itself can be an issue.
% We thus investigated other related characteristics.

>>>>

We have implemented domain fronting in a system called \meek,
a pluggable transport for Tor.
\meek\ combines fronting with a proxy server that encodes a TCP stream
as a sequence of HTTP requests and responses.
The \meek\ server's external interface is that of an ordinary web server.
Communication with it is enabled through domain fronting.
The server receives requests, decodes them, and feeds their payloads into a Tor relay,
and returns downstream data in the HTTP response.
A censor watching the communication sees only a sequence of HTTPS requests to an allowed domain.
but which actually arrive at a special web server on a Tor relay.
\meek, or something based on it,
has been adopted by other circumvention systems including Lantern and Psiphon.

@@

We have developed domain fronting into a full-fledged circumvention system called \meek,
implemented as a Tor pluggable transport~\cite{pt}.
\meek\ combines fronting with an HTTP-based tunneling proxy:
upstream data are transformed into a sequence of HTTP requests,
which are fronted in order to reach a proxy server.
The server decodes the requests and feeds their payloads
into a local Tor relay.
Downstream data received from the Tor relay
are returned to the client as HTTP responses
through the same fronted channel.
\meek's architecture appears in Figure~\ref{fig:architecture}.
Section~\ref{sec:architecture} describes its workings in detail.

@@

\meek\ has been built into an alpha version of Tor Browser,
and has seen use by a small number of users.
Our deployment uses Google App Engine,
with the hidden actual domain \urll{meek-reflect.appspot.com}
hidden by the front \urll{www.google.com}.
Section~\ref{sec:deployment} discusses other systems \meek\ can work with
and other deployment scenarios.
In addition to the Tor pluggable transport,
systems based on \meek\ are now in use by other circumvention systems
including Psiphon~\cite{psiphon} and Lantern~\cite{lantern}.

% \meek\ is designed to have features attractive in a circumvention transport.
% It is easy to use, not requiring the configuration of any bridge addresses.
% In Tor Browser, users need only select ``meek''
% from a pulldown menu in order to use it.
% It resists blocking by address and by content,
% Section~\ref{sec:discussion}

Domain fronting and HTTPS take care of two big circumvention challenges,
namely hiding the destination and obscuring the contents of the message.
There remain other, more subtle, meta-attributes of communication
that could serve as a basis for blocking.
For example, the handshake is a fingerprintable part of TLS.
Section~\ref{sec:browserextension} describes how we use a web browser extension as an instrument for making HTTPS requests,
in order that \meek's TLS and HTTPS characteristics
match those of a browser as closely as possible.
One of our goals for \meek\ is to force the censor
to employ more sophisticated, expensive, and error-prone statistical tests
to classify traffic as allowed or prohibited,
rather than simple domain blacklists or deep packet inspection;
to force the frontier of censorship
to be a frontier not of simple in-line packet filters,
but of probabilities and false positives.
A preliminary analysis of \meek's resistance to detection
based on traffic characteristics like packet size and timing
appears in Section~\ref{sec:trafficanalysis}.
The analysis is based on comparing traffic traces of \meek
with samples of HTTPS traffic at an Internet router.

@@

Flash proxy~\cite{flashproxy} resists address blocking by
conscripting web users as temporary proxies. Proxies last only as long as a web
user stays on a page, so the pool of proxies is constantly changing.
If one of them is blocked, there is soon another to replace it.
Flash proxy's approach to address blocking is in a sense
the opposite of \meek's:
where flash proxy uses many cheap, disposable, individually blockable proxies,
\meek\ uses just a few high-value front domains on hard-to-block network infrastructure.
A quirk of the browser proxy model is that
the client must be able to receive a TCP connection; in particular it
must not be behind network address translation~(NAT), which limits flash proxy's usefulness.
Part of the flash proxy protocol requires the client to send
a small amount of unblockable data in a process called rendezvous.
The default rendezvous mechanism has used domain fronting through App Engine since 2013~\cite{flashproxy-reg-appspot}.
Flash proxy itself does nothing to defend against DPI.
Connections between censored clients and browser-based proxies use
WebSocket, a meta-protocol running on HTTP,
but inside the WebSocket framing is the ordinary Tor protocol.
% There exists a prototype transport that attempts to get both
% content-based and address-based blocking resistance by obfuscating traffic
% with obfsproxy before sending it through flash proxy~\cite{obfs-flash}.
% However it is limited because it is not
% possible to obfuscate the outermost WebSocket layer;
% the censor could decide simply to block all WebSocket.

@@

GoAgent~\cite{goagent} is a direct inspiration for \meek\ in its use of App
Engine and Host header--based domain fronting.
Traffic is fronted by the Google frontend server
and delivered to its destination by a specialized app running on App Engine.
GoAgent uses the ``domainless'' fronting model without SNI for most target domains.
GoAgent doesn't use an additional general-purpose proxy after fronting;
rather, HTTP and HTTPS URLs are fetched directly from the App Engine servers,
meaning that GoAgent is limited to carrying HTTP and HTTPS traffic,
and the contents of all communications are revealed to App Engine.
Users of GoAgent upload their own personal copy of the proxy code to App Engine,
which is free of charge as long as they do not exceed a bandwidth quota.
According to a May 2013 survey~\cite{collateral-freedom},
GoAgent was the circumvention tool most used in
China, with 35\% of survey respondents having used it in the previous month.
This figure is higher than that of paid~(29\%) and free VPNs~(18\%), and far
above that of other special-purpose tools like Tor~(2.9\%) and Psiphon~(2.5\%).
Use of GoAgent in China was disrupted starting in the beginning of June~2014
when all Google services (including GoAgent's front domains) were blocked~\cite{cn-google-block}.
\meek\ over App Engine was similarly affected.
% Users identified reliability, speed, and ease of installation as the most important features of a circumvention tool.

@@

Psiphon~\cite{psiphon} is a network of many one-hop proxies,
with encryption and traffic obfuscation between client and server.
Psiphon uses domain fronting based on \meek\ as one of its blocking defenses since June~2014~\cite{psiphon-meek-merge}.
Lantern~\cite{lantern} uses a network of proxies running on volunteer computers;
proxy addresses are shared only with trusted friends in order to make them difficult to enumerate.
Lantern~1.4 is planned to use domain fronting inspired by \meek~\cite{lantern-1.3.1}.

@@

% CORDON? Say how \meek\ would be classified in it?

@@

Section~\ref{sec:discussion} shows what happens when some
of these assumptions are violated;
specifically what happens
when the intermediate web service's frontend server is inside the censor's network
and when the censor controls a certificate authority.
That section also describes the use of \meek\ apart from Tor.

@@

The components of the system are shown in Figure~\ref{fig:architecture}.
The parts that are new in \meek
are the programs \meekclient\ and \meekserver,
which are the pluggable-transports~\cite{pt} interface between Tor and \meek.
% All the programs are free software, naturally,
% and may be downloaded from the \meek\ home page at
% \url{https://trac.torproject.org/projects/tor/wiki/doc/meek}.

@@

When \meek\ is used with Google App Engine, one other component is needed.
It is a small ``reflector'' web app that simply copies any request
it receives and forwards it to an instance of \meekserver\ running on a bridge.
App Engine cannot directly run a Tor bridge,
so we bounce the requests to somewhere that can.
The reflector app emulates the behavior of an origin-pull CDN,
which also simply copies and forwards a request to the origin server
when the response is not already cached.

The main technical challenge is handling a TCP stream
that has been split up into a sequence of HTTP requests and responses.
The body of each HTTP request and HTTP response carries
a small chunk of upstream or downstream communication.
\meekserver\ must handle many clients at once,
and therefore maintains many open connections to the local Tor process,
one for each active client.
When a new request arrives, the server must determine which
open session it belongs to
(or whether it is a brand-new client needing a new session).
In TCP, different streams are distinguished by their
(source~IP, source port, dest~IP, dest~port) tuple,
but that doesn't work for \meek\ for two reasons:
the source IP of the requests is that of the intermediate web service,
not that of the client;
and a logical stream is chopped into multiple independent HTTP requests,
so the source port is always changing.
Rather, each client generates a random 256-bit session ID,
which it sends with each of its requests in a special
X-Session-Id header.
\meekserver, when it sees a session ID for the first time,
opens up a new connection to the local Tor process
and associates the connection and ID in a cache.
Subsequent requests with the
same session ID will reuse the same Tor connection.
Sessions are closed after a period of inactivity.
Figure~\ref{fig:protocol} shows a sample of the protocol.

@@

\x14\x03\x03\x00\x01\x01\x16\x03\x03\x00\x40\x06\x84\x25...
\end{verbatim}
\end{quote}
\caption{
Requests and responses in the \meek\ HTTP protocol.
The session ID is randomly generated by the client.
Request/response bodies contain successive chunks of a Tor TLS stream
(\texttt{\textbackslash{}x16\textbackslash{}x03\textbackslash{}x01\textbackslash{}x02}
is the beginning of a TLS ClientHello message).
The second POST request is an empty polling request.
The messages shown here is encrypted inside HTTPS until after
it has been fronted,
so the censor cannot use the
Host and X-Session-Id headers for classification.
}
\label{fig:protocol}
\end{figure}

The underlying TCP stream is broken into chunks so that
There must therefore be some way of making sure that chunks
are correctly reassembled at the other end,
in order and without gaps and duplicates.
\meek\ takes a naive approach: requests and responses are strictly serialized.
The client doesn't send a second chunk of data
(i.e, make another HTTPS request) until it has
receive the response to the first request.
The underlying stream is simply the concatenation
of chunks in the order they arrive.
Doing it this way is simple and guarantees correctness,
but has performance drawbacks because there is a full round-trip
between every send.
The performance drawbacks are not inherent to the design:
it is domain fronting, not HTTP encoding, that is the fundamental strength of the system.
Section~\ref{sec:futurework} describes more efficient encodings
that enable multiple requests in parallel.

HTTP is fundamentally a request-based protocol.
There is no way for the server to ``push'' data to the client without
having first received a request.
In order to enable the server to send back data,
\meek\ uses one of two techniques.
The first is polling:
every so often the client sends a request with an empty payload
if it has nothing else to send.
The polling interval starts short (100~ms) and grows exponentially
up to a maximum of 5~s.
% Implemented in Psiphon's version.
The other technique,
implemented in Psiphon's version of \meek,
uses long-lived persistent HTTP connections.
When the server sends a response, it keeps the connection open,
continually appending data to the response body while it has anything to send.
When the server receives a new request from the same client,
it closes any response it has open to the client and starts a new response.
This second technique doesn't work on all services:
notably Google App Engine doesn't support streaming downloads of this kind.

@@

Figure~\ref{fig:ciphersuites} shows examples of how TLS client
implementations may differ.
\meekclient\ is written in the Go programming language,
which has a custom TLS library~\cite{golang-crypto/tls};
Figure~\ref{fig:ciphersuites:golang}
shows how it would appear with no TLS camouflage.
Figures~\ref{fig:ciphersuites:firefox} and~\ref{fig:ciphersuites:chrome},
which are browsers, are different; the browsers are also unlike each other.
A censor could block an uncamouflaged \meek\ using Go's fingerprint,
if it considered the collateral damage resulting from blocking other Go programs to be slight enough.

@@

The use of a browser extension brings benefits beyond TLS camouflage.
It means \meek\ inherits other traffic characteristics of the browser:
for instance
how often it resolves DNS names,
its connection reuse,
and its HTTP keepalive behavior.
The Firefox extension has special advantages
when \meek\ is used with Tor Browser
because Tor Browser
is a modified version of Firefox.
We can use the same browser executable for both the browser the user interacts with (Tor Browser)
and the one providing TLS camouflage (a headless Firefox),
saving space in distribution packages
and sparing the user from having to separately configure a browser to run the extension.
In Tor Browser,
the headless Firefox is started and stopped transparently
when \meek\ is activated and deactivated.

@@

CloudFlare (\url{https://www.cloudflare.com/}),
not to be confused with CloudFront,
is a CDN also marketed as protection against
denial-of-service attacks.
It appears that any domain name on CloudFlare
can front for any other, even custom domains;
however it is not obvious which one is best to use as a front.
The front domain needs to be popular
(causing high collateral damage if blocked),
or else the censor may call our bluff and simply block the domain entirely.
It is doubly bad if that happens because not only is circumvention foiled,
some unsuspecting third part has just had their web site blocked.
A solution may be to round-robin through
a pool of domain names;
or to use ``domainless'' fronting that doesn't send SNI.
Though CloudFlare supports domain fronting,
its terms of service~\cite{cloudflare-terms}
seem to prohibit the kind of tunneled proxying that \meek\ does:
\begin{quote}
\textsc{Section 10: Limitation on non-HTML caching}\\
You acknowledge that CloudFlare's Service is offered as a platform to cache and
serve web pages and websites and is not offered for other purposes
\ldots\ you understand and agree to use the Service solely
for the purpose of hosting and serving web pages\ldots
\end{quote}

@@

One of our goals in developing \meek\ is to force
the censor to use relatively expensive statistical classifiers
to effect blocking---generally, to increase the cost of censorship.
We believe \meek\ as described is resistant to the ``easy''
forms of blocking, namely IP address and DNS blocking,
simple pattern-based DPI,
and active probing.
We hope that the censor will have to resort to measuring
more subtle features of the communication like
the packet length distribution and interpacket timing,
or injecting traffic at the risk of causing collateral damage.
In this section we provide a preliminary analysis
of \meek's resistance to such attacks.
Specifically, we consider three traffic features:
packet length distribution,
number of simultaneous connections,
and connection lifetime.

The issue of statistical traffic analysis is a general one~\cite{trafficmorphing},
and mostly orthogonal to \meek's main idea, domain fronting.
It may be that the problem is
best solved by a modular component not
necessarily specifically designed for \meek.

% Advantage is that we are probably proxying web traffic.
As \meek\ is based on HTTPS,
we compare traffic traces of \meek\ against
traces of ``ordinary'' HTTPS traffic.
We did a packet capture
automatically browsing the home pages
of the top 500 Alexa web sites using \meek,
with a firewall in place so that no extraneous traffic was included.
The used \meek\ in Tor Browser,
with the browser camouflage described in Section~\ref{sec:browserextension},
and Google App Engine as the intermediate web service.
The \meek\ trace is 687~megabytes in all
and covers about 4.5 hours of network activity.
Our representative of ordinary HTTPS traffic
is a sanitized trace of 10 minutes of HTTPS traffic
% anon
from Lawrence Berkeley National Laboratory (LBL),
comprising data to and from TCP port 443 on any Google server.
% Mention the non-google if it appears in a figure.
The trace contains packet headers only, not payloads
were replaced by an incrementing counter.
The LBL trace consists 313~megabytes of packet headers,
not payloads, destined for TCP port 443 on any Google server.
The original IP addresses were masked by being
replaced by a counter before we received the trace.

\begin{figure}
\centering
\includegraphics[width=\linewidth]{datalen.pdf}
\caption{
Comparison of TCP payload length distributions
between ordinary HTTPS connections to Google services
from the LBL traffic trace,
and \meek\ running on App Engine, fronted through www.google.com.
% The histogram's bin width is 5~bytes.
}
\label{fig:datalen}
\end{figure}

\subsection{Packet length}
Figure~\ref{fig:datalen}
compares the packet length distribution of both traces in both directions.
Table~\ref{tab:datalen} summarizes the most common values.
In both traces, about 38\% of packets have an empty payload, mostly ACKs.
There is a small peak at the usual TCP Maximum Segment Size
of 1460 bytes.
The concentration of values near 1418 bytes
may be caused by Google servers' sizing of TLS records so they fit within TCP segments.
% https://github.com/joyent/node/issues/6889
% http://mailman.nginx.org/pipermail/nginx-devel/2013-December/004703.html
Conspicuous in the \meek\ trace are a small number of
likely packet sizes,
and the lack of a cluster of small payload lengths of around 50 bytes.
Both of these characteristics are probably artifacts
of Tor's fixed cell size and the nearly fixed-size HTTP headers
added by \meekclient\ and \meekserver.

% Output of datalen.R.
%
% LBL
%          0       1430       1418         41       1416       1460       1260
% 0.37665361 0.09120402 0.08493944 0.06090732 0.03101247 0.02941974 0.02021770
%       1400       1359         33
% 0.01673740 0.01126137 0.01100281
%
% meek
%        1418           0        1460         396         196        1024
% 0.405280243 0.376703906 0.071561089 0.019905460 0.018484996 0.014868083
%         811         783         151        1263
% 0.012312668 0.007811963 0.007031241 0.006569205
\begin{table}[ht]
\normalsize
\centering
\begin{tabular}{r r >{\qquad} r r}
\multicolumn{2}{c}{LBL Google HTTPS} & \multicolumn{2}{>{\qquad}c}{\meek\ on App Engine} \\
0 bytes & 37.6\% & 1418 bytes & 40.5\% \\
1430 bytes & 9.1\% & 0 bytes & 37.7\% \\
1418 bytes & 8.5\% & 1460 bytes & 7.2\% \\
41 bytes & 6.1\% & 396 bytes & 2.0\% \\
1416 bytes & 3.1\% & 196 bytes & 1.8\% \\
1460 bytes & 2.9\% & 1024 bytes & 1.5\%
\end{tabular}
\caption{The most common TCP payload lengths.}
\label{tab:datalen}
\end{table}

% David: I don't think the following paragraph is true.
% Almost all the length>1400 packets are Google→client, not client→Google,
% as you can see if you split the histogram up by direction.
%
% To explain the phenomenon, recall that we use browsers to handle HTTPS connections for \meek\ in order
% to hide TLS handshake characteristics.
% Browsers also apply techniques like HTTP pipelining to improve performance. Since \meek\ is always communicating with
% the same Google frontend server, the browser will keep the persistent TLS connection. In addition, small requests 
% can be batched into a large chunk before being sent. This explains why large packets are mostly seen from the trace that
% records \meek's traffic.
% In contrast, normal users may not have persistent connections to Google. For example, a user may search a keyword on
% Google, click a result, and then close the tab that displays search results. The browser may close the 
% connection immediately after the user leaves the Google web page. Next time the user browses Google search, the browser 
% opens a new connection. In this case, small requests do not have such opportunity for batching.

% These browser techniques improve performance, but also pose unexpected consequences. 
% Although \meek\ alters the packet size distribution of underlying Tor traffic, 
% the censor may be aware of the distribution of \meek\ itself. 
% Additionally, the persistent connection itself can be an issue.
% We thus investigated other related characteristics.
